Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-01-13 ms/S2_appendix.tex
tweaks to figure caption

>>>>

\begin{figure}[!ht]
  \includegraphics[width=\textwidth]{../figures/fig_S2_4.pdf}
\caption{{\bf Effects of contact heterogeneity and vital dynamics.}
This figure matches Fig 3 in main text, but displays the
summary statistics of the modified explicit models (models with contact heterogeneity and vital dynamics).
For each model, its summary statistics are plotted on the univariate plot using different shapes.
All models were simulated using the baseline parameters.
}
\label{fig:fig3aug}
\end{figure}
